---
title: "Assigment 1"
output: github_document

---
```{css parameter,  echo=FALSE}
pre {
  max-height: 200px;
  overflow-y: auto;
  overflow-x: auto;
}

pre[class] {
  max-height: 100px;
}
```

```{r setup, include=TRUE, cache=TRUE, tidy=TRUE}
knitr::opts_chunk$set(echo = TRUE, comment=NA)
knitr::opts_chunk$set(error = TRUE, cache = TRUE)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, reticulate, here, haven, descriptr)

use_python("/usr/local/bin/python3")
```

## Downloading the Raw Data
We start by downloading and processing the [HCRIS](https://github.com/Nixoncandiales/Econ771/tree/main/Assigments/AS%201/Code/HCRIS), [POS](https://github.com/Nixoncandiales/Econ771/tree/main/Assigments/AS%201/Code/POS), and [ACA](https://github.com/Nixoncandiales/Econ771/tree/main/Assigments/AS%201/Code/ACA) raw data sets. Then calling the output data from`HCRIS_Data.txt` and `pos_lastyear.v12.dta`

```{r import-data-hcris, tidy=TRUE, echo=FALSE, cache=TRUE, comment=NA}
if (!exists("data_hcris")) data_hcris <- read.delim(here("Assigments", "As 1", "Output", "HCRIS", "HCRIS_Data.txt"))
ds_screener(data_hcris)
```
```{r import-data-pos, include=TRUE, tidy=TRUE, echo=TRUE, cache=TRUE, comment=NA}
if (!exists("data_pos")) data_pos <- read_stata(here("Assigments", "As 1", "Output", "POS", "pos_lastyear.v12.dta"))
ds_screener(data_pos)
```


### Summary Statistics
Provide and discuss a table of simple summary statistics showing the mean, standard deviation, min, and max of hospital total revenues and uncompensated care over time.

From the `HCRIS_data.txt` we select the variables *provider_number*, *year*, *tot_uncomp_care_charges*, *tot_pat_rev* 

```{r select-data, tidy=TRUE, echo=TRUE, cache=TRUE, comment=NA}
data_hcris %>% 
  select(pn=provider_number, year, uncomp_care, tot_uncomp_care_charges, tot_pat_rev) %>% 
  as_tibble()
```
Then we group by year and calculate the summary statistics.

```{r summary-statistics-uncoomp-care, tidy=TRUE, echo=TRUE, cache=TRUE, comment=NA, warning=FALSE}
sum_unc_care <- data_hcris %>% 
  select(provider_number, year, uncomp_care, tot_uncomp_care_charges, tot_pat_rev) %>%
  mutate(tot_uncomp_care_charges = pmax(tot_uncomp_care_charges,uncomp_care, na.rm=TRUE)) %>%
  group_by(year) %>% 
  summarise(
    Mean = mean(tot_uncomp_care_charges, na.rm = TRUE), 
    SD = sd(tot_uncomp_care_charges, na.rm = TRUE), Min = min(tot_uncomp_care_charges, na.rm = TRUE), 
    Max = max(tot_uncomp_care_charges, na.rm = TRUE)
  ) %>% 
  drop_na(Mean)

sum_unc_care
```

```{r summary-statistics-tot-rev, tidy=TRUE, echo=TRUE, cache=TRUE, comment=NA}
sum_tot_rev <- data_hcris %>% 
  select(provider_number, year, tot_uncomp_care_charges, tot_pat_rev) %>% 
  group_by(year) %>% 
  summarise(
    Mean = mean(tot_pat_rev, na.rm = TRUE), 
    SD = sd(tot_pat_rev, na.rm = TRUE), Min = min(tot_pat_rev, na.rm = TRUE), 
    Max = max(tot_pat_rev, na.rm = TRUE)
  ) %>% 
  drop_na(Mean)

sum_tot_rev
```

```{r plot, tidy=TRUE, echo=TRUE, cache=TRUE, comment=NA}
plot1 <-
  sum_unc_care %>% 
  ggplot(aes(x = year, y = Mean)) + 
  geom_point()
plot1

plot2 <-
  sum_tot_rev %>% 
  ggplot(aes(x = year, y = Mean)) + 
  geom_point()
plot2
```

### By Ownership Type
Create a figure showing the mean hospital uncompensated care from 2000 to 2018. Show this trend separately by hospital ownership type (private not for profit and private for profit).
```{r, include=FALSE}
library(tidyverse)
```

```{r merge, warning=FALSE }
data_merged <- 
  left_join(data_hcris %>%
              mutate(unc_care = pmax(tot_uncomp_care_charges,uncomp_care, na.rm=TRUE)) %>% 
              select(pn=provider_number, year, unc_care, hos_rev=tot_pat_rev) %>% 
              as.tibble() %>%
              drop_na(unc_care)
            ,
            data_pos %>%
              select(pn, nonprofit, forprofit, govt) %>%
              mutate_at('pn', as.integer)
            ,
            by="pn") 
```

```{r echo=FALSE}
data_merged
```
```{r plot3, warning=FALSE }
data_merged %>%
  filter(year<=2018, nonprofit==1) %>%
  select(pn, year, unc_care, nonprofit) %>%
  group_by(year) %>%
  summarise(Mean = mean(unc_care, na.rm = TRUE)) %>% 
  ggplot(aes(x = year, y = Mean)) + 
  geom_line() -> plot3
```

```{r echo=FALSE}
plot3
```

```{r plot4, warning=FALSE }
data_merged %>%
  filter(year<=2018, forprofit==1) %>%
  select(pn, year, unc_care, nonprofit) %>%
  group_by(year) %>%
  summarise(Mean = mean(unc_care, na.rm = TRUE)) %>% 
  ggplot(aes(x = year, y = Mean)) + 
  geom_line() -> plot4
```

```{r echo=FALSE}
plot4
```

```{r delete, include=FALSE}
rm(data1,data2, sum_tot_rev, sum_unc_care)
```