---
title: "Assigment 1"
output: github_document
always_allow_html: true
---
```{css parameters, include=FALSE}
pre {
  max-height: 200px;
  overflow-y: auto;
  overflow-x: auto;
}

pre[class] {
  max-height: 100px;
}
```

```{r setup, include=FALSE, cache=TRUE, tidy=TRUE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA)
knitr::opts_chunk$set(error = TRUE, cache = T)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, reticulate, here, haven, descriptr, HonestDiD, did, fixest, RColorBrewer, patchwork, ggthemes, DT, plotly)
```

## Downloading the Raw Data
We start by downloading and processing the [HCRIS](https://github.com/Nixoncandiales/Econ771/tree/main/Assigments/AS%201/Code/HCRIS), [POS](https://github.com/Nixoncandiales/Econ771/tree/main/Assigments/AS%201/Code/POS), and [ACA](https://github.com/Nixoncandiales/Econ771/tree/main/Assigments/AS%201/Code/ACA) raw data sets. The processed data sets are located in the [**Output**]((https://github.com/Nixoncandiales/Econ771/tree/main/Assigments/AS%201/Output)) folder under `HCRIS_Data.txt`, `pos_lastyear.v12.dta`, and `acs_medicare.txt` . We import those data sets in our file and inspect them as follows.

```{r import-data-hcris, tidy=TRUE, echo=TRUE, cache=TRUE, comment=NA}
if (!exists("data_hcris")) data_hcris <- read.delim(here("Assigments", "As 1", "Output", "HCRIS", "HCRIS_Data.txt"))
ds_screener(data_hcris)
```
After a quick screening of the HCRIS data we can see the missing values are significantly high which suggest some variables are recorded differently across time and forms. It is of particular interest the variables `uncomp_care` and `tot_uncomp_care_charges` which are of our main interest. After reviewing the codebook we confirmed in fact these two variables are the same but coded different across forms. 

```{r import-data-pos, include=TRUE, tidy=TRUE, echo=TRUE, cache=TRUE, comment=NA}
if (!exists("data_pos")) data_pos <- read_stata(here("Assigments", "As 1", "Output", "POS", "pos_lastyear.v12.dta"))
ds_screener(data_pos)
```

From the provider of services data set we do not evidence missing data problems. We can observe if a particular POS went out of the market by either closing or merging and the respectively date of the event. It is to note the identifier variable is `pn` which is recorded as a character differs in the HCRIS data set `provider_number` which is coded as numerical. 

```{r import-data-medicaid, tidy=TRUE, echo=TRUE, cache=TRUE, comment=NA}
if (!exists("data_aca")) data_aca <- read.delim(here("Assigments", "As 1", "Output", "ACA", "acs_medicaid.txt"))
ds_screener(data_aca)
```

Finally, from the medicare data set we see the states that expanded the mandate and the date of event. Also, it is to note that the state identifier is not recorded in the same format across data sets.

## Summary Statistics
Provide and discuss a table of simple summary statistics showing the mean, standard deviation, min, and max of hospital total revenues and uncompensated care over time.

From the `HCRIS_data.txt` we select the variables `provider_number`, `year`, `uncomp_care`, `tot_uncomp_care_charges`, `tot_pat_rev`. We create a new variable that stores the uncompensated care records, then we group by year and calculate the summary statistics as follows.

```{r summary-stats, tidy=TRUE, echo=TRUE, cache=TRUE, comment=NA, warning=FALSE}
data_hcris %>% 
  rowwise() %>% 
  mutate(hosp_rev = tot_pat_rev, unc_care = 
           sum(tot_uncomp_care_charges,uncomp_care, na.rm=TRUE)) %>%
  mutate_at(c('unc_care'), ~na_if(., 0)) %>%
  select(pn=provider_number, year, unc_care, hosp_rev )  %>%
  filter(!(is.na(unc_care) & is.na(hosp_rev)) & ((year>=2003)&(year<=2019)))-> data_hcris1

data_hcris1 %>%
  group_by(year) %>%
  summarise_at(c('unc_care', 'hosp_rev'),list(mean = mean, sd = sd, min = min, max = max), na.rm=T) %>%
  knitr::kable()
```

```{r plot-summary-stats, tidy=TRUE, echo=TRUE, cache=TRUE, comment=NA, warning=FALSE}
data_hcris1 %>%
  ggplot(aes(x = year, y = unc_care, group=year)) + 
  geom_boxplot() + 
  theme_tufte() -> plot1

data_hcris1 %>%
  ggplot(aes(x = year, y = hosp_rev, group=year)) + 
  geom_boxplot() + 
  theme_tufte()  -> plot2

plot1 / plot2
```


## By Ownership Type
Create a figure showing the mean hospital uncompensated care from 2000 to 2018. Show this trend separately by hospital ownership type (private not for profit and private for profit).
```{r load-libraries, include=FALSE}
library(tidyverse)
library(ggthemes)
```

```{r merge, warning=FALSE }
data_hcris1 <- data_hcris1 %>% filter(year>=2003 & year<=2019) #subset by the years

data_pos1 <- data_pos %>%
  select(pn = unique('pn'), nonprofit, forprofit, active) %>%
  mutate_at('pn', as.integer) %>% # This will force strings ID into NA (those are no-hospital POS)
  filter( pn >0 ) %>% #remove NA cases
  mutate(own_typ = case_when(nonprofit == 0  & forprofit == 0  ~ 'other',
                             nonprofit == 0  & forprofit == 1  ~ 'forprofit',
                             nonprofit == 1  & forprofit == 0  ~ 'nonprofit')) %>% # Create a factor variable for ownership type
  filter((own_typ == 'forprofit') | (own_typ == 'nonprofit' )  ) %>%  # discard govt and other forms of ownership
  select(pn, own_typ) # Select the variables to merge

hcris_1 <- left_join(data_hcris1, data_pos1, by="pn") %>% 
  mutate_at('own_typ',  replace_na, 'other') %>% # replace NA by other
  select(pn, year, unc_care, own_typ) %>%
  filter(!(own_typ == 'other'))
##This last line of code is because if I include other types of ownerships I am getting duplicated cases.. i need to dig a bit more into this behavior. 
```

```{r hcris-1-table, echo=FALSE, , comment=NA}
hcris_1%>% head %>% knitr::kable()
```

```{r plot-own-typ, warning=FALSE, comment=NA, message = FALSE}
hcris_1 %>%
  group_by(year, own_typ) %>%
  summarise_at(c('unc_care'), list(unc_care_mean = mean), na.rm=T) %>%
  ggplot(aes(x=year, y=unc_care_mean, color=own_typ)) +
  geom_point(size = 1) +
  geom_smooth(aes(fill = own_typ), size = 1) +
  theme_tufte()
```


```{r delete, include=FALSE}
rm(data_hcris1,data_pos1)
```

## Did identification strategy
Using a simple DD identification strategy, estimate the effect of Medicaid expansion on hospital uncompensated care using a traditional two-way fixed effects (TWFE) estimation:
\begin{equation}
y_{it} = \alpha_{i} + \gamma_{t} + \delta D_{it} + \varepsilon_{it},
(\#eq:dd)
\end{equation}
where $D_{it}=1(E_{i}\leq t)$ in Equation \@ref(eq:dd) is an indicator set to 1 when a hospital is in a state that expanded as of year $t$ or earlier, $\gamma_{t}$ denotes time fixed effects, $\alpha_{i}$ denotes hospital fixed effects, and $y_{it}$ denotes the hospital's amount of uncompensated care in year $t$. Present four estimates from this estimation in a table: one based on the full sample (regardless of treatment timing); one when limiting to the 2014 treatment group (with never treated as the control group); one when limiting to the 2015 treatment group (with never treated as the control group); and one when limiting to the 2016 treatment group (with never treated as the control group). Briefly explain any differences.

## Event Study
Estimate an "event study" version of the specification in part 3:
\begin{equation}
y_{it} = \alpha_{i} + \gamma_{t} +\sum_{\tau < -1} D_{it}^{\tau} \delta_{\tau} + \sum_{\tau>=0} D_{it}^{\tau} \delta_{\tau} + \varepsilon_{it},
(\#eq:event)
\end{equation}
where $D_{it}^{\tau} = 1(t-E_{i}=\tau)$ in Equation \@ref(eq:event) is essentially an interaction between the treatment dummy and a relative time dummy. In this notation and context, $\tau$ denotes years relative to Medicaid expansion, so that $\tau=-1$ denotes the year before a state expanded Medicaid, $\tau=0$ denotes the year of expansion, etc. Estimate with two different samples: one based on the full sample and one based only on those that expanded in 2014 (with never treated as the control group).

## SA specification
Sun and Abraham (SA) show that the $\delta_{\tau}$ coefficients in Equation \@ref(eq:event) can be written as a non-convex average of all other group-time specific average treatment effects. They propose an interaction weighted specification:
\begin{equation}
y_{it} = \alpha_{i} + \gamma_{t} +\sum_{e} \sum_{\tau \neq -1} \left(D_{it}^{\tau} \times 1(E_{i}=e)\right) \delta_{e, \tau} + \varepsilon_{it}.
(\#eq:iwevent)
\end{equation}
Re-estimate your event study using the SA specification in Equation \@ref(eq:iwevent). Show your results for $\hat{\delta}_{e, \tau}$ in a Table, focusing on states with $E_{i}=2014$, $E_{i}=2015$, and $E_{i}=2016$.

## Event Study - SA specification
Present an event study graph based on the results in part 5. Hint: you can do this automatically in `R` with the `fixest` package (using the `sunab` syntax for interactions), or with `eventstudyinteract` in `Stata`. These packages help to avoid mistakes compared to doing the tables/figures manually and also help to get the standard errors correct.

## Callaway and Sant'Anna Specification (CS)
Callaway and Sant'Anna (CS) offer a non-parametric solution that effectively calculates a set of group-time specific differences, $ATT(g,t)= E[y_{it}(g) - y_{it}(\infty) | G_{i}=g]$, where $g$ reflects treatment timing and $t$ denotes time. They show that under the standard DD assumptions of parallel trends and no anticipation, $ATT(g,t) = E[y_{it} - y_{i, g-1} | G_{i}=g] - E[y_{it} - y_{i,g-1} | G_{i} = \infty]$, so that $\hat{ATT}(g,t)$ is directly estimable from sample analogs. CS also propose aggregations of $\hat{ATT}(g,t)$ to form an overall ATT or a time-specific ATT (e.g., ATTs for $\tau$ periods before/after treatment). With this framework in mind, provide an alternative event study using the CS estimator. Hint: check out the `did` package in `R` or the `csdid` package in `Stata`.

## Rambachan and Roth (RR)
Rambachan and Roth (RR) show that traditional tests of parallel pre-trends may be underpowered, and they provide an alternative estimator that essentially bounds the treatment effects by the size of an assumed violation in parallel trends. One such bound RR propose is to limit the post-treatment violation of parallel trends to be no worse than some multiple of the pre-treatment violation of parallel trends. Assuming linear trends, such a violation is reflected by $$\Delta(\bar{M}) = \left\{ \delta : \forall t \geq 0, \lvert (\delta_{t+1} - \delta_{t}) - (\delta_{t} - \delta_{t-1}) \rvert \leq \bar{M} \times \max_{s<0} \lvert (\delta_{s+1} - \delta_{s}) - (\delta_{s} - \delta_{s-1}) \rvert \right\}.$$ Using the `HonestDiD` package in `R` or `Stata`, present a sensitivity plot of your CS ATT estimates using $\bar{M} = \{0, 0.5, 1, 1.5, 2\}$. Check out the GitHub repo [here](https://github.com/pedrohcgs/CS_RR) for some help in combining the `HonestDiD` package with CS estimates.

## Discussion
Discuss your findings and compare estimates from different estimators (e.g., are your results sensitive to different specifications or estimators? Are your results sensitive to violation of parallel trends assumptions?).

## Reflections
Reflect on this assignment. What did you find most challenging? What did you find most surprising? 
