---
title: "Asigment 1"
author: "Nixon Candiales"
date: \today
output: 
  pdf_document:
    latex_engine: lualatex
    keep_tex: true
link-citations: yes
header-includes:
  - \usepackage{fontspec}
  - \usepackage{polyglossia}
  - \setmainlanguage[babelshorthands=true]{german}
  - \setmainfont{merriweather}
  - \setsansfont{Montserrat}
  - \geometry{vmargin=1in,hmargin=1.25in}
  - \usepackage{xcolor}
  - \usepackage{titlesec}
  - \definecolor{Blue}{HTML}{2F5496}
  - \titleformat{\section}{\Large\sffamily\color{Blue}}{}{0pt}{}
  - \titleformat{\subsection}{\large\sffamily\color{Blue}}{}{0pt}{}
  - \titlespacing\section{0pt}{24pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}
  - \titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{2pt plus 2pt minus 2pt}
  - \usepackage{parskip}
  - \usepackage{siunitx}
  - \newcolumntype{d}{S[input-symbols = ()]}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage[default]{sourcesanspro}
  - \usepackage[T1]{fontenc}
fontsize: 12pt
mainfont: SourceSansPro
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup-load-output, include=FALSE, warning=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, here, did, fixest, stargazer, tinytex, rmarkdown, knitr, kableExtra, plotly, knitr, bookdown, modelsummary, xtable)
knitr::opts_knit$set(root.dir = here("Assigments", "AS 1"))
here::i_am("Main.Rmd")
load(here("Output", "Output.Rdata"))
options("modelsummary_format_numeric_latex" = "plain")
knitr::opts_chunk$set(echo = TRUE)
```

# Summary Statistics

Provide and discuss a table of simple summary statistics showing the
mean, standard deviation, min, and max of hospital total revenues and
uncompensated care over time.

```{r Fig-1, include=TRUE, echo=FALSE, warning=FALSE, comment=NA, message=FALSE}
plot1
plot2
```

```{r Tab-1, include=TRUE, echo=FALSE, warning=FALSE, comment=NA, results='asis'}
#All year summary
df %>% 
  ungroup() %>%
  summarise_at(c("unc_care", "hosp_rev"), 
               list(mean = mean, sd = sd, min = min, max = max), na.rm = TRUE) -> table1
#Over time Summary
df %>%
  group_by(year) %>%
  summarise_at(c('unc_care', 'hosp_rev'),
               list(mean = mean, sd = sd, min = min, max = max), na.rm=T) %>%
  relocate(starts_with("unc"), starts_with("hosp"))-> table2

#Rbind both Tables
table1$year <- "2003-2019"
table1 <- table1 %>% relocate(year)
table <- rbind(table2,table1) %>% relocate(year)

#Display the Table in Latex
kable(table, 
      digits=2, 
      format = "latex", 
      align="crrrrrrrr",
      col.names = c("year", "Mean", "Sd", "Min", "Max",
                           "Mean", "Sd", "Min", "Max"),
      longtable = T, booktabs = T, caption = "Hospital Summary Statistics") %>% 
kable_styling(latex_options = c("scale_down", "hold_position"), 
              position = "center")  %>% 
add_header_above(c(" ", "Uncompensated Care" = 4, "Total Revenue" = 4))
```

Create a figure showing the mean hospital uncompensated care from 2000
to 2018. Show this trend separately by hospital ownership type (private
not for profit and private for profit).

```{r Fig-2, include=TRUE, echo=FALSE, warning=FALSE, comment=NA, message=FALSE}
plot3
```

# TWFE Specification

Using a simple DD identification strategy, estimate the effect of
Medicaid expansion on hospital uncompensated care using a traditional
two-way fixed effects (TWFE) estimation:

```{=tex}
\begin{equation}\label{eq:dd}
y_{it} = \alpha_{i} + \gamma_{t} + \delta D_{it} + \varepsilon_{it},
\end{equation}
```
where $D_{it}=1(E_{i}\leq t)$ in Equation \ref{eq:dd} is an indicator
set to 1 when a hospital is in a state that expanded as of year $t$ or
earlier, $\gamma_{t}$ denotes time fixed effects, $\alpha_{i}$ denotes
hospital fixed effects, and $y_{it}$ denotes the hospital's amount of
uncompensated care in year $t$. Present four estimates from this
estimation in a table: one based on the full sample (regardless of
treatment timing); one when limiting to the 2014 treatment group (with
never treated as the control group); one when limiting to the 2015
treatment group (with never treated as the control group); and one when
limiting to the 2016 treatment group (with never treated as the control
group). Briefly explain any differences.

```{r Tab-2, include=TRUE, echo=FALSE, warning=FALSE, comment=NA, message=FALSE}
modelsummary(mod.twfe,
          title = "Two Way Fixed Effects",
          label="tab-4",
          table.placement = "H",
          column.labels = c("M1", "M2", "M3"),
          model.numbers = FALSE,
          header=FALSE,
          stars = TRUE,
          output = "latex")

```

# Event Study Specification

Estimate an "event study" version of the specification in part 3:

```{=tex}
\begin{equation}\label{eq:event}
y_{it} = \alpha_{i} + \gamma_{t} +\sum_{\tau < -1} D_{it}^{\tau} \delta_{\tau} + \sum_{\tau>=0} D_{it}^{\tau} \delta_{\tau} + \varepsilon_{it},
\end{equation}
```
where $D_{it}^{\tau} = 1(t-E_{i}=\tau)$ in Equation \ref{eq:event} is
essentially an interaction between the treatment dummy and a relative
time dummy. In this notation and context, $\tau$ denotes years relative
to Medicaid expansion, so that $\tau=-1$ denotes the year before a state
expanded Medicaid, $\tau=0$ denotes the year of expansion, etc. Estimate
with two different samples: one based on the full sample and one based
only on those that expanded in 2014 (with never treated as the control
group).

# SA Specification

Sun and Abraham(SA) show that the $\delta_{\tau}$ coefficients in
Equation \@ref(eq:event) can be written as a non-conxvex average of all
other group-time specific average treatment effects. They propose an
interaction weighted specification:

```{=tex}
\begin{equation}
y_{it} = \alpha_{i} + \gamma_{t} +\sum_{e} \sum_{\tau \neq -1} \left(D_{it}^{\tau} \times 1(E_{i}=e)\right) \delta_{e, \tau} + \varepsilon_{it}.
(\#eq:iwevent)
\end{equation}
```
Re-estimate your event study using the SA specification in Equation
\@ref(eq:iwevent). Show your results for $\hat{\delta}_{e, \tau}$ in a
Table, focusing on states with $E_{i}=2014$, $E_{i}=2015$, and
$E_{i}=2016$.

Present an event study graph based on the results in part 5. Hint: you
can do this automatically in `R` with the `fixest` package (using the
`sunab` syntax for interactions), or with `eventstudyinteract` in
`Stata`. These packages help to avoid mistakes compared to doing the
tables/figures manually and also help to get the standard errors
correct.

# CS Specification

Callaway and Sant'Anna (CS) offer a non-parametric solution that
effectively calculates a set of group-time specific differences,
$ATT(g,t)= E[y_{it}(g) - y_{it}(\infty) | G_{i}=g]$, where $g$ reflects
treatment timing and $t$ denotes time. They show that under the standard
DD assumptions of parallel trends and no anticipation,
$ATT(g,t) = E[y_{it} - y_{i, g-1} | G_{i}=g] - E[y_{it} - y_{i,g-1} | G_{i} = \infty]$,
so that $\hat{ATT}(g,t)$ is directly estimable from sample analogs. CS
also propose aggregations of $\hat{ATT}(g,t)$ to form an overall ATT or
a time-specific ATT (e.g., ATTs for $\tau$ periods before/after
treatment). With this framework in mind, provide an alternative event
study using the CS estimator. Hint: check out the `did` package in `R`
or the `csdid` package in `Stata`.

# RR Specification

Rambachan and Roth (RR) show that traditional tests of parallel
pre-trends may be underpowered, and they provide an alternative
estimator that essentially bounds the treatment effects by the size of
an assumed violation in parallel trends. One such bound RR propose is to
limit the post-treatment violation of parallel trends to be no worse
than some multiple of the pre-treatment violation of parallel trends.
Assuming linear trends, such a violation is reflected by
$$\Delta(\bar{M}) = \left\{ \delta : \forall t \geq 0, \lvert (\delta_{t+1} - \delta_{t}) - (\delta_{t} - \delta_{t-1}) \rvert \leq \bar{M} \times \max_{s<0} \lvert (\delta_{s+1} - \delta_{s}) - (\delta_{s} - \delta_{s-1}) \rvert \right\}.$$
Using the `HonestDiD` package in `R` or `Stata`, present a sensitivity
plot of your CS ATT estimates using $\bar{M} = \{0, 0.5, 1, 1.5, 2\}$.
Check out the GitHub repo [here](https://github.com/pedrohcgs/CS_RR) for
some help in combining the `HonestDiD` package with CS estimates.

# Discussion

Discuss your findings and compare estimates from different estimators
(e.g., are your results sensitive to different specifications or
estimators? Are your results sensitive to violation of parallel trends
assumptions?).

# Reflection

Reflect on this assignment. What did you find most challenging? What did
you find most surprising?

```{r Figures, include=TRUE, echo=FALSE, warning=FALSE, comment=NA, message=FALSE}
plot1

plot2

plot3

iplot(mod.esct, main= "Effect of Medicaid Eaxpansion on Uncompensated
Care")

iplot(mod.esdt, main= "Effect of Medicaid Eaxpansion on Uncompensated
Care")

coefplot(mod.sa, main= "Effect of Medicaid Eaxpansion on Uncompensated
Care")

ggdid(mod.cs)

ggdid(mod.cs.event,
title = "Event-study aggregation \\n DiD using never-treated as
comparison group")

cs_HDiD_smooth

cs_HDiD_relmag
```

```{r table-4, include=TRUE, echo=FALSE, warning=FALSE, comment=NA, results='asis'}
modelsummary(mod.twfe,
          title = "Two Way Fixed Effects long format",
          label="tab-4",
          table.placement = "H",
          column.labels = c("M1", "M2", "M3"),
          model.numbers = FALSE,
          header=FALSE,
          stars = TRUE,
          output = "latex")

modelsummary(mod.esct,
          title = "Event Study Common Treatment",
          label="tab-5",
          table.placement = "H",
          column.labels = c("M1", "M2", "M3"),
          model.numbers = FALSE,
          header=FALSE,
          stars = TRUE,
          output = "latex")

modelsummary(mod.esdt,
          title = "Even Study Staggered",
          label="tab-6",
          table.placement = "H",
          column.labels = c("M1", "M2", "M3"),
          model.numbers = FALSE,
          header=FALSE,
          stars = TRUE,
          output = "latex")


modelsummary(mod.sa,
          title = "SA especification",
          label="tab-7",
          table.placement = "H",
          column.labels = c("M1", "M2", "M3"),
          model.numbers = FALSE,
          header=FALSE,
          stars = TRUE,
          output = "latex")

modelsummary(mod.cs,
          title = "CS specification",
          label="tab-8",
          table.placement = "H",
          column.labels = c("M1", "M2", "M3"),
          model.numbers = FALSE,
          header=FALSE,
          output = "latex")

modelsummary(mod.cs.event,
          title = "CS specification Event Study",
          label="tab-9",
          table.placement = "H",
          column.labels = c("M1", "M2", "M3"),
          model.numbers = FALSE,
          header=FALSE,
          output = "latex")
```
