---
title: "Econ771 - Empirical Exercise 1"
author: "Nixon Torres Candiales"
date: \today
output: 
  pdf_document:
    latex_engine: lualatex
    keep_tex: true
link-citations: yes
linestretch: 1.25
header-includes:
  - \usepackage{amssymb}
  - \usepackage{amsmath}
  - \usepackage{subfig}
fontsize: 12pt
font: Latin Modern Math
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup-load-output, include=FALSE, warning=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, here, did, fixest, stargazer, tinytex, rmarkdown, knitr, kableExtra, plotly, knitr, bookdown, modelsummary, xtable, tinytex)
knitr::opts_knit$set(root.dir = here("Assigments", "AS 1"))
here::i_am("Main.Rmd")
load(here("Output", "Output.Rdata"))
options("modelsummary_format_numeric_latex" = "plain")
knitr::opts_chunk$set(echo = TRUE)
```

# Summary Statistics

Provide and discuss a table of simple summary statistics showing the
mean, standard deviation, min, and max of hospital total revenues and
uncompensated care over time. We start first by downloading and merging
all the Data from the Github repository. We present the distribution of
the variables of interest, Uncompensated care and Hospital Revenue over
time

```{r Fig-1, include=TRUE, echo=FALSE, cache=FALSE, results=FALSE, warning=FALSE,  comment=FALSE, message= FALSE,  fig.cap = "Box-plot", fig.subcap=c('Uncompensated Care', 'Revenue'), out.width='.49\\linewidth', fig.asp=1, fig.ncol = 2 }
plot1
plot2
```


We see evidence of negative entries in uncompensated care as well as
extreme atypical values that might be caused by mistyping. As such, we
subset the data by not including the top and bottom 0.5% of the
observations. The mean, standard deviation, and minimum and maximum
values across the years are presented in table 1 of summary statistics.

```{r Tab-1, include=TRUE, echo=FALSE, warning=FALSE, comment=NA, results='asis'}
#Display the Table in Latex
kable(table, 
      digits=2, 
      format = "latex", 
      align="crrrrrrrr",
      col.names = c("year", "Mean", "Sd", "Min", "Max",
                           "Mean", "Sd", "Min", "Max"),
      longtable = T, booktabs = T, caption = "Hospital Summary Statistics") %>% 
kable_styling(latex_options = c("hold_position"), 
              position = "center")  %>% 
add_header_above(c(" ", "Uncompensated Care" = 4, "Total Revenue" = 4))
```

Next, we create a figure showing the mean hospital uncompensated care
from 2003 to 2019. We show this trend separately by hospital ownership
type in figure 3. We present an smooth trend to easily identify shifts
after the adoption of medicare expansion in 2014. We can see an abrupt
bump from years 2010 to 2011, this might be due to the adoption of the
new form and a change in the way to measure uncompensated care \^[after
2010 uncompensated care = total uncompensated care - total uncompensated
partial payments + bad debt]. Also, in recent years, it seems for-profit
hospitals get to provide more uncompensated care than not for profit
hospitals.

```{r Fig-2, include=TRUE, echo=FALSE, fig.cap = "Evolution of Uncompensated Care Over Time", warning=FALSE,comment=NA, message=FALSE, label="Fig-2"}
plot3
```

\newpage

# TWFE Specification

Using a simple DD identification strategy, we estimate the effect of
Medicaid expansion on hospital uncompensated care using a traditional
two-way fixed effects (TWFE) estimation:

\begin{equation}
\label{eq:dd}
y_{it} = \alpha_{i} + \gamma_{t} + \delta D_{it} + \varepsilon_{it},
\end{equation}

where $D_{it}=1(E_{i}\leq t)$ in Equation \ref{eq:dd} is an indicator
set to 1 when a hospital is in a state that expanded as of year $t$ or
earlier, $\gamma_{t}$ denotes time fixed effects, $\alpha_{i}$ denotes
hospital fixed effects, and $y_{it}$ denotes the hospital's amount of
uncompensated care in year $t$. We present four estimates from this
estimation in table \ref{Tab-2}: one based on the full sample (1); one when limiting to the 2014 treatment group (2); 
one when limiting to the 2015
treatment group (3); and one when
limiting to the 2016 treatment group (3).

A first appreciation of our results indicate that the ATE of medicaid expansion on uncompensated care is negative. The point estimate varies when limiting the treatment sample for 2014 to 2016 as well as the confidence intervals but we get a consistent trend across the samples. We see the effect is larger when limiting the sample to the states that expanded in 2014.

```{r Tab-2, include=TRUE, echo=FALSE, warning=FALSE, comment=NA, message=FALSE, results='asis', label="Tab-2"}
dep_var <- c("Full Sample", "2014 Sample", "2015 Sample", "2016 Sample")
names(mod.twfe) <- c(dep_var)

modelsummary(mod.twfe,
          title = "Two Way Fixed Effects",
          style = "aer",
          label="Tab-2",
          table.placement = "H",
          column.labels = c("M1", "M2", "M3", "M4"),
          model.numbers = TRUE,
          header=FALSE,
          stars = TRUE,
          gof_omit = "R2 Adj.|BIC|AIC",
          output = "latex")%>% 
          #notes = list("Each column represents a different treatment sample used in the estimation")) %>% 
add_header_above(c(" ", "Uncompensated Care" = 4))
```


\newpage
# Event Study Specification

We estimate an event study version of the specification in part 3:

\begin{equation}
\label{eq:event}
y_{it} = \alpha_{i} + \gamma_{t} +\sum_{\tau < -1} D_{it}^{\tau} \delta_{\tau} + \sum_{\tau>=0} D_{it}^{\tau} \delta_{\tau} + \varepsilon_{it},
\end{equation}

where $D_{it}^{\tau} = 1(t-E_{i}=\tau)$ in Equation \ref{eq:event} is
 an interaction between the treatment indicator and a relative
time indicator. $\tau$ denotes years relative
to Medicaid expansion. In this case $\tau=-1$ denotes the year before a state
expanded Medicaid and the control group for those never treated. $\tau=0$ denotes the year of expansion, and so on.

Table \ref{Tab-3} presents the estimates for the common treatment time for the 2014 sample, whereas \ref{Tab-4} presents the estimates for the staggered intervention for the full sample. In both specifications the control group is formed by the never treated.
Also, we can observe in \ref{Fig-2} the event study coefficients plot. It is clear the drop in uncompensated care after the first year of the medicaid expansion. Also the ATT seems to increase as $\tau$ increases. We can see that the average treatment on the treated is the highest 5 years after the treatment.

```{r Tab-3, include=TRUE, echo=FALSE, warning=FALSE, comment=NA, message=FALSE, label="Tab-3", results='asis'}
   modelsummary(mod.es,
                title = "Event Study",
                style = "aer",
                table.placement = "H",
                column.labels = c("M1", "M2", "M3", "M4"),
                model.numbers = TRUE,
                header=FALSE,
                stars = TRUE,
                gof_omit = "R2 Adj.|BIC|AIC",
                output = "latex") %>% 
add_header_above(c(" ", "Uncompensated Care" = 2))
```   

```{r Tab-3b, include=TRUE, echo=FALSE, warning=FALSE, comment=NA, message=FALSE, label="Tab-3b", results='asis'}
# modelsummary(mod.esdt,
#                 title = "Event Estudy Full Sample",
#                 style = "aer",
#                 table.placement = "H",
#                 column.labels = c("M1", "M2", "M3", "M4"),
#                 model.numbers = TRUE,
#                 header=FALSE,
#                 stars = TRUE,
#                 gof_omit = "R2 Adj.|BIC|AIC",
#                 output = "latex")
```

```{r Fig-3a, include=TRUE, echo=FALSE, fig.cap = "Event Study", warning=FALSE,comment=NA, message=FALSE, label="Fig-3"}
iplot(mod.es, main= "Effect of Medicaid Eaxpansion on Uncompensated
Care")

legend("bottomleft", col = c(1, 2), pch = c(20, 17), legend = c("2014 Sample", "Full Sample"))
```

```{r Fig-3b, include=FALSE, evaluate=FALSE, echo=FALSE, cache=FALSE, results=FALSE, warning=FALSE,  comment=FALSE, message= FALSE,  fig.cap = "Event Study", fig.subcap=c('Sample 2014', 'Full Sample'), out.width='.49\\linewidth', fig.asp=1, fig.ncol = 2 }
# iplot(mod.esct, main= "Effect of Medicaid Eaxpansion on Uncompensated
# Care")
# iplot(mod.esdt, main= "Effect of Medicaid Eaxpansion on Uncompensated
# Care")
```
\newpage
# SA Specification

No we move to Sun and Abraham(SA) specification and estimate a non-conxvex average of all
other group-time specific average treatment effects. The interaction weighted specification is given by:

```{=tex}
\begin{equation}\label{eq:iwevent}
y_{it} = \alpha_{i} + \gamma_{t} +\sum_{e} \sum_{\tau \neq -1} \left(D_{it}^{\tau} \times 1(E_{i}=e)\right) \delta_{e, \tau} + \varepsilon_{it}.
\end{equation}
```
\ref{table-5} presents the Re-estimate coefficients for the event study using the SA specification. For this specification we focus on the states that expanded either on 2014, 2015 or 2016 and include those in the treatment group. Whereas the control group is formed by the never treated observations. Providers that are in a state that expanded after 2016 are not considered in this part. The coefficients presented in the table are $\hat{\delta}_{e, \tau}$.

```{r Tab-4, include=TRUE, echo=FALSE, warning=FALSE, comment=NA, message=FALSE, label="Tab-4", results='asis'}
modelsummary(mod.sa,
                title = "Event Estudy Sun and Abraham(SA) Specification",
                style = "aer",
                table.placement = "H",
                column.labels = c("M1", "M2", "M3", "M4"),
                model.numbers = TRUE,
                header=FALSE,
                stars = TRUE,
                gof_omit = "R2 Adj.|BIC|AIC",
                output = "latex") %>%
                #notes = list("Each column represents a different tratment sample")) %>% 
add_header_above(c(" ", "Uncompensated Care" = 3))
```
Also, \Ref{Fig-5} presents the coefficients plot for the SA specification. We can see how this smooth the pre-trend before the medicaid expansion. Under this especification we see the Uncompensated care is significatly declining even before the expansion. 

```{r Fig-4, include=TRUE, echo=FALSE, fig.cap = "Effect of Medicaid Eaxpansion on Uncompensated Care - SA Specification for different treatment samples", warning=FALSE,comment=NA, message=FALSE, label="Fig-4"}
coefplot(mod.sa, main= "Event Study SA Specification")
legend("topright", col = c(1, 2, 3), pch = c(20, 15, 17), 
       legend = c("2014", "2015", "2016"))
```




\newpage
# CS Specification

Callaway and Sant'Anna (CS) offer a non-parametric solution that
effectively calculates a set of group-time specific differences,
$ATT(g,t)= E[y_{it}(g) - y_{it}(\infty) | G_{i}=g]$, where $g$ reflects
treatment timing and $t$ denotes time. They show that under the standard
DD assumptions of parallel trends and no anticipation,
$ATT(g,t) = E[y_{it} - y_{i, g-1} | G_{i}=g] - E[y_{it} - y_{i,g-1} | G_{i} = \infty]$,
so that $\hat{ATT}(g,t)$ is directly estimable from sample analogs. CS
also propose aggregations of $\hat{ATT}(g,t)$ to form an overall ATT or
a time-specific ATT (e.g., ATTs for $\tau$ periods before/after
treatment). With this framework in mind, provide an alternative event
study using the CS estimator. Hint: check out the `did` package in `R`
or the `csdid` package in `Stata`.

```{r Fig-5, include=TRUE, echo=FALSE, cache=FALSE, results=FALSE, warning=FALSE,  comment=FALSE, message= FALSE,  fig.cap = "Callaway and Sant’Anna (CS) Specification", fig.subcap=c('ATT by Cohorts', 'Event Study'), out.width='.49\\linewidth', fig.asp=1, fig.ncol = 2 }
ggdid(mod.cs[[1]])

ggdid(mod.cs[[2]],
title = "Event-study aggregation \\n DiD using never-treated as
comparison group")
```

```{r Tab-6, include=TRUE, echo=FALSE, warning=FALSE, comment=NA, message=FALSE, label="Tab-6", results='asis'}
modelsummary(mod.cs[1], 
                shape = term + response ~ statistic,
                title = "DiD CS Specification",
                style = "aer",
                table.placement = "H",
                model.numbers = TRUE,
                header=FALSE,
                gof_omit = "R2 Adj.|BIC|AIC",
                output = "latex", 
                estimate  = "{estimate} [{conf.low}, {conf.high}]",
                statistic = NULL) %>%
  kable_styling(font_size = 6)
```

```{r Tab-7, include=TRUE, echo=FALSE, warning=FALSE, comment=NA, message=FALSE, label="Tab-7", results='asis'}
modelsummary(mod.cs[2],
                title = "ATT's based on event-study/dynamic aggregation:",
                style = "aer",
                table.placement = "H",
                column.labels = c("M1", "M2", "M3", "M4"),
                model.numbers = TRUE,
                header=FALSE,
                gof_omit = "R2 Adj.|BIC|AIC",
                output = "latex", 
                shape = term + response ~ statistic)
```

\newpage
# RR Specification

Rambachan and Roth (RR) show that traditional tests of parallel
pre-trends may be underpowered, and they provide an alternative
estimator that essentially bounds the treatment effects by the size of
an assumed violation in parallel trends. One such bound RR propose is to
limit the post-treatment violation of parallel trends to be no worse
than some multiple of the pre-treatment violation of parallel trends.
Assuming linear trends, such a violation is reflected by
$$\Delta(\bar{M}) = \left\{ \delta : \forall t \geq 0, \lvert (\delta_{t+1} - \delta_{t}) - (\delta_{t} - \delta_{t-1}) \rvert \leq \bar{M} \times \max_{s<0} \lvert (\delta_{s+1} - \delta_{s}) - (\delta_{s} - \delta_{s-1}) \rvert \right\}.$$
Using the `HonestDiD` package in `R` or `Stata`, present a sensitivity
plot of your CS ATT estimates using $\bar{M} = \{0, 0.5, 1, 1.5, 2\}$.
Check out the GitHub repo [here](https://github.com/pedrohcgs/CS_RR) for
some help in combining the `HonestDiD` package with CS estimates.

```{r Fig-6, include=TRUE, echo=FALSE, cache=FALSE, results=FALSE, warning=FALSE,  comment=FALSE, message= FALSE,  fig.cap = "Rambachan and Roth (RR) Specification", fig.subcap=c('Smooth', 'Relative Magnitude'), out.width='.49\\linewidth', fig.asp=1, fig.ncol = 2 }
cs_HDiD_smooth
cs_HDiD_relmag
```

\newpage
# Discussion

Discuss your findings and compare estimates from different estimators
(e.g., are your results sensitive to different specifications or
estimators? Are your results sensitive to violation of parallel trends
assumptions?).

Across all different specifications we see a robust result, the ATE is negative, that is the reduction in Uncomponsetad Care provided by hospitals is due to the exogenous policy shock, the expansion Medicaid across states. We have robust evidence to say this is a cusal effect. 

\newpage
# Reflection

Reflect on this assignment. What did you find most challenging? What did
you find most surprising?

The first challenge was to collect all data sets and merge them into one, which requires a few programming skills and institutional knowledge of the field. I encountered one specific problem while combining POS and HCRIS data since I was not aware of the possibility that providers changed the ownership compositions over time. I was not aware of this situation until very late.

A second challenge was implementing the HonestDiD package. My results were not interpretable or plausible when dealing with the original grid.

The main takeaways from this assignment is the importance of developing a transparent and reproducible workflow that allows to make the changes easily and improving my coding skills to avoid code repetition and improve accuracy and efficiency.